---
title: "Assignment 1"
output: html_document
---
``` Akash Bairagi (21227) ```
-------------------------------------------------------------------------------

```{r}
library("readr")
library("tidyverse")
library("moments")
insurance_data = read_csv("insurance.csv")
```

# EDA

### 1. Find the shape of the data,data type of individual columns
```{r}
dim(insurance_data)
names(insurance_data)
str(insurance_data)

```

### 2.Descriptive stats of numerical columns
```{r}

datanum = select_if(insurance_data, is.numeric)
summary(datanum)

```

### 3.Find the distribution of numerical columns and the asssociated skeweness
```{r}
datanum %>%
  gather() %>%
  group_by(key) %>%
  mutate(skewness = moments::skewness(value),
         label = paste0(key, "\n","Skewness: ", round(skewness, 2))) %>%
  ggplot(aes(value)) +
  facet_wrap(~ label, scales = "free", ncol = 2, strip.position = "bottom") +
  geom_histogram(aes(y = ..density..), binwidth = 1, fill = "grey") +
  geom_density(colour = "black")
```

### 4.Are there any outliers for Numeric features (Use Box Plots)
```{r}
FindOutliers <- function(data) {
  lowerq = quantile(data)[2]
  upperq = quantile(data)[4]
  iqr = IQR(data)
  uppThresh = (iqr * 1.5) + upperq
  lowThresh = lowerq - (iqr * 1.5)
  result <- which(data > uppThresh | data < lowThresh)
  return(length(result))
}

datanum %>%
  gather() %>%
  group_by(key) %>%
  mutate(outlier = FindOutliers(value),
         label = paste0(key, "\n","Outliers - ", outlier)) %>%
  ggplot(aes(y=value)) +
  facet_wrap(~ label, scales = "free", ncol = 2, strip.position = "bottom") +
  geom_boxplot()
```

# Data Visualization

### 1. Does Smokers pay more insurance amount than non-smokers? What are your observations ?
```{r}
res = setNames(aggregate(insurance_data['expenses'], list(insurance_data$smoker), mean), c("smoker","mean_insurance_amount"))
res[1,1]="non-smoker"
res[2,1]="smoker"
res
pie(res$mean_insurance_amount, res$smoker, main="Mean Insurace Amount")
```


Thus smokers pay More insurance than non-smokers.



### 3. Does People with Higher BMI pay Higher insurance amount than those with lower BMI ? What are your observations ?
```{r}
ggplot(insurance_data, aes(bmi, expenses)) +
geom_point()+
geom_smooth(method=lm)+
annotate(x=45, y=60000,
label=paste("R = ", round(cor(insurance_data$bmi, insurance_data$expenses),3)),
geom="text", size=4)
```

We cannot say with 100% confidence that People with Higher BMI pay Higher insurance amount than those with lower BMI. It depends on other conditions as well.


### 3. Can we comment about the effect of age on insurance amount being paid?
```{r}
ggplot(insurance_data, aes(age, expenses)) +
  geom_point()+
  geom_smooth(method=lm)+
  annotate(x=45, y=60000,
           label=paste("R = ", round(cor(insurance_data$age, insurance_data$expenses),3)),
           geom="text", size=4)
```

Therefore, we observe that higher the age higher is the insurance amount.


### 4. is Some Region paying more insurance charges than other regions ?
```{r}
res = setNames(aggregate(insurance_data['expenses'], list(insurance_data$region), mean), c("region","mean"))
res= merge(setNames(aggregate(insurance_data['expenses'], list(insurance_data$region), sum), c("region","sum")), res)
res
ggplot(res, aes(region, sum)) +
geom_bar(stat= "identity")+
geom_text(aes(label= signif(mean)),color='pink', position=position_stack(vjust = 0.5))
```

Southeast region pays more insurance charges copared to  other regions.



### 5. What is the distribution of charges ? is it skewed ? What are your observations ?
```{r}
ggplot(insurance_data, aes(expenses)) +
geom_density(colour = "black")+
annotate(x=40000, y=4e-05,
label=paste("Skewness = ", moments::skewness(insurance_data$expenses)),
geom="text", size=4)
```



### 6. What's the inference from the Pairplot of Numeric Variables
```{r}
library(GGally)
ggpairs(data=datanum)+theme_bw()
```



### 7. Save the Pairplot as Jpeg/SVG files.
```{r}
jpeg("tips_pairs_plot.jpg")
```